Logarithmic Space Verifiers on NP-complete

### 2019-11-16 doc/manuscript.tex
Fixed some details in doc

\begin{definition}
\label{definition}
The class $LNL$ contains those languages that are decided by a nondeterministic logarithmic space Turing machine $N$ such that for every instance $x = yz$ of these languages, there are a prefix and suffix substrings $y$ and $z$ where $N$ moves strictly deterministically on $y$ and strictly nondeterministically on $z$ while strictly deterministically means there is no a possible nondeterministic step and strictly nondeterministically means there is at least one nondeterministic step.
\end{definition}

Sauerhoff have shown the class $BNL$ of languages recognizable by nondeterministic logarithmic space Turing machine, that only use nondeterministic moves before reading their input (``nondeterminism at the beginning") \cite{MS03}.

@@

\begin{proof}
We have that $NL \subseteq LNL$, because the prefix $y$ of an instance $x = yz$ could be the empty string. Certainly, the languages in the class $L \subseteq NL$ could be decided by nondeterministic logarithmic space Turing machines that exactly do a single nondeterministic step after the original acceptance state choosing nondeterministically the same acceptance state within two equals choices from the original and modified deterministic logarithmic space Turing machines which decide these languages (this is assuming the prefix string $y$ is the empty string in the instances $x = yz$). Moreover, we have that $LNL \subseteq NL$, because the languages in $LNL$ are decided by nondeterministic logarithmic space Turing machines. Since $NL \subseteq LNL$ and $LNL \subseteq NL$, then the complexity class $LNL$ is equal to $NL$. However, we can state that $BNL \neq LNL$, because there is no possible way for an instance $x = yz$ when the prefix $y$ is the empty string in some languages in $BNL$, such that we could move strictly nondeterministically on $y$ (that would be a ``nondeterminism at the beginning") and move strictly deterministically on the nonempty string $z$ over the Definition \ref{definition} of $LNL$. Hence, we obtain that $BNL \neq NL$ by transitivity. Nevertheless, Sauerhoff have also shown that $L \subseteq BNL \subseteq NL$ \cite{MS03}. Consequently, we prove the complexity class $L$ is not equal to $NL$.
\end{proof}

>>>>

\begin{definition}
\label{definition}
The class $LNL$ contains those languages that are decided by a nondeterministic logarithmic space Turing machine $N$ such that for every instance $x = yz$ of these languages, there are a prefix and suffix substrings $y$ and $z$ where $N$ moves strictly deterministically on $y$ and strictly nondeterministically on $z$ when strictly deterministically means there is no a possible nondeterministic step and strictly nondeterministically means there is at least one nondeterministic step on the computation.
\end{definition}

Sauerhoff has shown the class $BNL$ of languages recognizable by nondeterministic logarithmic space Turing machine, that only use nondeterministic moves before reading their input (``nondeterminism at the beginning") \cite{MS03}.

@@

\begin{proof}
We have that $NL \subseteq LNL$, because the prefix $y$ of an instance $x = yz$ could be the empty string. Certainly, all the languages in the class $NL$ could be decided by nondeterministic logarithmic space Turing machines such that they always do a single nondeterministic step after the original acceptance state choosing nondeterministically the same acceptance state within two equals choices from the original and modified deterministic or nondeterministic logarithmic space Turing machines which decide these languages (this is assuming the prefix string $y$ is the empty string in the instances $x = yz$). Moreover, we have that $LNL \subseteq NL$, because the languages in $LNL$ are decided by nondeterministic logarithmic space Turing machines. Since $NL \subseteq LNL$ and $LNL \subseteq NL$, then the complexity class $LNL$ is equal to $NL$. However, we can state that $BNL \neq LNL$, because there is no possible way over the Definition \ref{definition} of $LNL$ for an instance $x = yz$ when the prefix $y$ is the empty string in some languages in $BNL$, such that we could move strictly nondeterministically on $y$ (that would be a ``nondeterminism at the beginning") and move strictly deterministically on the nonempty string $z$. Hence, we obtain that $BNL \neq NL$ by transitivity. Nevertheless, Sauerhoff has also shown that $L \subseteq BNL \subseteq NL$ \cite{MS03}. Consequently, we prove the complexity class $L$ is not equal to $NL$.
\end{proof}
